---
title: "R Notebook"
output: html_notebook
---

My goal for this project is to learn the functions of R and use it to manipulate and analyze the WIFL dataset. 

Reading in the file
```{r}
library(readr)
  WIFL_Metadata <-read_csv("~/Desktop/WIFLProject/WIFL_Metadata.csv")
  panel1 <- read_delim("~/Desktop/WIFLProject/panel1.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
  panel2 <- read_delim("~/Desktop/WIFLProject/panel2.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```

Joining WIFL Meta Data with Panel 1 and 2 SNP calls
```{r}
library(tidyverse)
  WIFLPanel1 <- WIFL_Metadata %>% left_join(panel1, by = "Field_Number")
  WIFLPanel1_2 <- WIFLPanel1 %>% left_join(panel2, by = "Field_Number")
```

Filtering Breeders
```{r}
library(tidyverse)
  library(ggplot2)
  Breeders <- filter(WIFLPanel1_2, Stage == 'Breeding')
  ggplot(Breeders, aes(x = Lat, y = Long, color = Group)) +     
  geom_point()
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
